\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Added projection for Five Gaussian cluster

>>>>

<!--Projection with tSNE-->
```{r}
#| label: five-gau-proj-tsne-model

training_data_gau <- read_rds("data/five_gau_clusters/data_five_gau_training.rds")

tsne_data_gau <- read_rds("data/five_gau_clusters/tsne_data_five_gau_61.rds")
gau1_scaled_obj <- gen_scaled_data(
  data = tsne_data_gau)
tsne_gau_scaled <- gau1_scaled_obj$scaled_nldr

## Compute hexbin parameters
num_bins_x_gau1 <- 14
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x",
  q = 0.16
)

df_bin_centroids_gau1 <- gau1_model$df_bin_centroids
df_bin_gau1 <- gau1_model$df_bin

## Triangulate bin centroids
tr1_object_gau1 <- tri_bin_centroids(
  df_bin_centroids_gau1, x = "c_x", y = "c_y")
tr_from_to_df_gau1 <- gen_edges(
  tri_object = tr1_object_gau1)

# tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
#   filter(row_number() != 76) |>
#   filter(row_number() != 34)

tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
  filter(row_number() != 115) |>
  filter(row_number() != 139)

## Compute 2D distances
distance_gau1 <- cal_2d_dist(
  tr_coord_df = tr_from_to_df_gau1,
  start_x = "x_from",
  start_y = "y_from",
  end_x = "x_to",
  end_y = "y_to",
  select_vars = c("from", "to", "distance"))

## To find the benchmark value
benchmark_gau1 <- find_lg_benchmark(
  distance_edges = distance_gau1,
  distance_col = "distance")

trimesh_removed_gau1 <- vis_rmlg_mesh(
  distance_edges = distance_gau1,
  benchmark_value = benchmark_gau1,
  tr_coord_df = tr_from_to_df_gau1,
  distance_col = "distance")

## Hexagonal binning to have regular hexagons
hb_obj_gau1 <- hex_binning(
  data = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  q = 0.16)

tsne_data_with_hb_id <- hb_obj_gau1$data_hb_id

df_all_gau1 <- dplyr::bind_cols(training_data_gau |> dplyr::select(-ID),
                                  tsne_data_with_hb_id)

### Define type column
df <- df_all_gau1 |>
  dplyr::select(tidyselect::starts_with("x")) |>
  dplyr::mutate(type = "data") ## original dataset

df_b <- df_bin_gau1 |>
  dplyr::filter(hb_id %in% df_bin_centroids_gau1$hexID) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b <- df_b[match(df_bin_centroids_gau1$hexID, df_b$hb_id),] |>
  dplyr::select(-hb_id)

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)

projection <- cbind(
  c(0.28321,-0.28851,-0.67413,0.39226),
  c(-0.70800,-0.44269,0.04835,0.26867))

five_gau_proj_tsne_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.15, 0.15)) +
  ylim(c(-0.15, 0.15))
```

```{r}
#| label: fig-five-gau-projs
#| fig-cap: "(a) tSNE"

five_gau_proj_tsne_model
```

### 2024-08-14 paper.tex
Added projection for Five Gaussian cluster

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-52-1.pdf}
\end{center}

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-five-gau-projs-1.pdf}

\caption{\label{fig-five-gau-projs}(a) tSNE}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-54-1.pdf}
\end{center}
